Demographics: The Sound of Teaching Music 1

### 2020-02-10 script/RNotebook/questionnaire.Rmd
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Error Rate of excluded participants
```{r errorRate_excluded, echo = FALSE}
# Information about excluded participants due to errorRate (SubNr 16 was excluded but due to not errorRate but tempo deviation)
# Error Rate = the number of trials which contain any mistake (Not the number of mistakes in a trial)
errorRate_mean_exc <- mean(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_sd_exc <- sd(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*sqrt((length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])-1)/length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16]))*100 #biased sd for the current data
errorRate_median_exc <- median(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_min_exc <- min(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_max_exc <- max(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100

>>>>

### Error Rate of excluded participants
```{r er_excluded, echo = FALSE}
# Information about excluded participants due to errorRate (SubNr 16 was excluded but due to not errorRate but tempo deviation)
# Error Rate = the number of trials which contain any mistake (Not the number of mistakes in a trial)
errorRate_mean_exc <- mean(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_sd_exc <- sd(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*sqrt((length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])-1)/length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16]))*100 #biased sd for the current data
errorRate_median_exc <- median(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_min_exc <- min(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_max_exc <- max(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
